Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-05 paper.tex
Batch of tweaks to plots
Update plots to two-column format

\begin{figure*}
    \includegraphics{figures/mutations-perf}
\caption{\label{fig-mutations-perf} Time required to run
\texttt{sim\_mutations} on tree sequences generated
by \texttt{sim\_ancestry} (with a population size of $10^4$
and recombination rate of $10^{-8}$) for varying (haploid) sample
size and sequence length. We ran 10 replicate mutation simulations
each for three different mutation rates, and report the average
CPU time required (Intel Core i7-9700).
(A) Holding sequence length fixed at 10 megabases and varying the
number of samples (tree tips) from 10 to 100,000.
(B) Holding number of samples fixed at 1000, and varying the sequence
length from 1 to 100 megabases.}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics{figures/gc-perf}
\end{center}
\caption{\label{fig-gc-perf}Comparison of simulation performance
using \msprime\ (\texttt{sim\_ancestry}), \SimBac, and \FastSimBac\ for varying
(haploid) sample sizes,
and the current estimates
for \textit{E.~coli} parameters~\citep{lapierre2016the}:
a 4.6Mb genome, $N_e = 1.8\times 10^8$, gene conversion rate of $8.9\times 10^{-11}$
per base and mean tract length of $542$.
We report (A) the total CPU time and (B) maximum memory usage
averaged over 5 replicates (Intel Xeon E5-2680 CPU).
We did not run \SimBac\ beyond first two data points because
of the very long running times.}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics{figures/sweeps-perf}
\end{center}
\caption{\label{fig-selection-perf}Comparison of selective sweep simulation
performance in \msprime\ (\texttt{sim\_ancestry}) and \discoal\ (Intel Xeon Gold 6148 CPU).
We report the average CPU time and maximum memory usage when simulating 3
replicates for 100 diploid samples in a model
with a single selective sweep in its history, where the beneficial
allele had a selection coefficient of $s=0.05$,
a per-base recombination rate of $10^{-8}$, population size of $N=10^4$,
and sequence length varying from 100kb--3000kb.}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics{figures/dtwf-perf}
\end{center}
\caption{\label{fig-dtwf-perf} Comparison of Discrete Time Wright-Fisher
(DTWF) simulation performance in \msprime\ (\texttt{sim\_ancestry})
and \ARGON\ (Intel Xeon E5-2680 CPU).
We ran simulations with a population size of $10^4$ and
recombination rate of $10^{-8}$, with 500 diploid samples
and varying sequence length.
We report (A) total CPU time and (B) maximum memory usage;
each point is the average over $5$ replicate simulations.
We show observations for \ARGON, \msprime's DTWF implementation (``DTWF'')
and a hybrid simulation of 100 generations of the DTWF followed by
the standard coalescent with recombination (``DTWF + Hudson'').
We ran \ARGON\ with a mutation rate of $0$ and with minimum output options,
with a goal of measuring only ancestry simulation time.
Memory usage for \msprime's DTWF and hybrid simulations are very similar.
}
\end{figure*}

>>>>

\begin{figure}
    \includegraphics{figures/mutations-perf}
\caption{\label{fig-mutations-perf} Time required to run
\texttt{sim\_mutations} on tree sequences generated
by \texttt{sim\_ancestry} (with a population size of $10^4$
and recombination rate of $10^{-8}$) for varying (haploid) sample
size and sequence length. We ran 10 replicate mutation simulations
each for three different mutation rates, and report the average
CPU time required (Intel Core i7-9700).
(A) Holding sequence length fixed at 10 megabases and varying the
number of samples (tree tips) from 10 to 100,000.
(B) Holding number of samples fixed at 1000, and varying the sequence
length from 1 to 100 megabases.
\the\columnwidth}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics{figures/gc-perf}
\end{center}
\caption{\label{fig-gc-perf}Comparison of simulation performance
using \msprime\ (\texttt{sim\_ancestry}), \SimBac, and \FastSimBac\ for varying
(haploid) sample sizes,
and the current estimates
for \textit{E.~coli} parameters~\citep{lapierre2016the}:
a 4.6Mb genome, $N_e = 1.8\times 10^8$, gene conversion rate of $8.9\times 10^{-11}$
per base and mean tract length of $542$.
We report (A) the total CPU time and (B) maximum memory usage
averaged over 5 replicates (Intel Xeon E5-2680 CPU).
We did not run \SimBac\ beyond first two data points because
of the very long running times.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics{figures/sweeps-perf}
\end{center}
\caption{\label{fig-selection-perf}Comparison of selective sweep simulation
performance in \msprime\ (\texttt{sim\_ancestry}) and \discoal\ (Intel Xeon Gold 6148 CPU).
We report the average CPU time and maximum memory usage when simulating 3
replicates for 100 diploid samples in a model
with a single selective sweep in its history, where the beneficial
allele had a selection coefficient of $s=0.05$,
a per-base recombination rate of $10^{-8}$, population size of $N=10^4$,
and sequence length varying from 100kb--3000kb.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics{figures/dtwf-perf}
\end{center}
\caption{\label{fig-dtwf-perf} Comparison of Discrete Time Wright-Fisher
(DTWF) simulation performance in \msprime\ (\texttt{sim\_ancestry})
and \ARGON\ (Intel Xeon E5-2680 CPU).
We ran simulations with a population size of $10^4$ and
recombination rate of $10^{-8}$, with 500 diploid samples
and varying sequence length.
We report (A) total CPU time and (B) maximum memory usage;
each point is the average over $5$ replicate simulations.
We show observations for \ARGON, \msprime's DTWF implementation (``DTWF'')
and a hybrid simulation of 100 generations of the DTWF followed by
the standard coalescent with recombination (``Hybrid'').
We ran \ARGON\ with a mutation rate of $0$ and with minimum output options,
with a goal of measuring only ancestry simulation time.
Memory usage for \msprime's DTWF and hybrid simulations are very similar.
}
\end{figure}
